The task allocation problem solution proposed by \textit{Schwarzrock et al.} in \cite{MAS07} was modeled as a generalized assignment problem (GAP)\cite{ferreira2007swarm}. The goal of this proposal is to maximize the total capability of the agents using a probabilistic approach \cite{theraulaz1998response}. Their solution relies on the combination of GAP and swarm intelligence \cite{MOEA07}, called swarm-GAP, using a token based communication protocol. The proposal presented by \textit{Schwarzrock et al.}\cite{MAS07} results in three variants based on swarm-GAP, as listed in the following:

\begin{itemize}
   \item \textit{Allocation Loop (AL)}: a control list of visited agents is used and the token runs while there is available tasks. To avoid the infinite loop, the agent registers if it has any resource available to perform a new task before resend the token. Only the agent with free resources will receive the token;
   \item \textit{Sorting and Allocation Loop (SAL)}: sorts the list of tasks based on the tendency($\textrm{T}_{\theta_{ij}}$) of execution by the UAV. This prevents the first agent, during the token exchange, from being assigned all tasks, not considering others UAVs more suitable to perform some of these tasks and producing better results. 
   \item \textit{Limit and Allocation Loop (LAL)}: increases SAL's behavior and defines a task selection limit per UAV in each round to prevent a greedy strategy and idle agents;
\end{itemize}

Algorithms \ref{algo:swarm-gap} and \ref{algo:swarm-gap2} show the pseudo code of SAL and AL. The LAL algorithm code was not listed due to its similarity with SAL and the lines \ref{line:ALini} to \ref{line:ALfim} of the Algorithm \ref{algo:swarm-gap} are common to all of them.

\begin{algorithm}[h!t]
	\caption{Pseudo code - Allocation loop (AL) (from Schwarzrock et al.\cite{MAS07})}
	\label{algo:swarm-gap}
	
	\SetAlgoLined
	\DontPrintSemicolon
	\SetKwBlock{Loop}{loop}{end loop}
	\SetKwFor{ForAll}{for all}{do}{end for}
	\SetNlSty{text}{}{:}
	\SetNlSkip{0.3em}
	
	Receive Token\; \label{line:recebe}
	
	Compute available resources $r_i $ \; \label{line:compute_r}
	\ForAll{ available tasks }{ \label{line:forall}
		Compute capability $k_{ij}$\; \label{line:compute_k}
		Compute tendency $T_{\theta_{ij}(st)}$ \;  \label{line:compute_t}
		\If{ roulette() $< T_{\theta_{ij}(st)}$ and $r_i \geq c_j $}{ \label{line:ini_ifalgo1}
			Allocate task $j$ to agent $i$ \; \label{line:aloca_sgap}
			Decrease resource $r_i $\; \label{line:decrease_r} \label{line:fim_ifalgo1}
		}
	}
	
	Mark agent as visited in the token\; \label{line:ALini}
	\If{there are still available tasks}{
		Inform token if it has availability to perform any one of these tasks\; \label{line:informadisponibilidade}
		\If{all agents already receive the token}{
			Clean the list of visited agents\;
			Fill list of visited agents with the unavailable agents\;
		}
		Send the token to a not yet visited agent\; \label{line:ALfim}
	}
\end{algorithm}

To represent the agent will to perform a task, the proposed algorithms define an attribute called $stimulus (st)$. This variable balances the weight among the distance to the task and sensor quality to perform it. \textit{Ferreira et al.}\cite{ferreira2007swarm} provided evidence that the most suitable value to this variable, in most situations, is $0.6$. Equation \ref{eq:tendencia} shows the calculation of task execution tendency using the $stimulus$ value and the threshold $\theta$. Higher $stimulus$ indicates that less specialized agents will perform the tasks. On the other hand, if $stimulus$ is lower, the task will be done by a more specialized agent.\cite{bonabeau1999swarm}. 

The agent threshold $\theta$ is defined by the Equation \ref{eq:limiar} and depends on the agent's capability $k_{ij}$ to perform a task. The capability of an agent $i$ to perform each task $j$ belonging to a set $J$ of available tasks, is defined by Equation \ref{eq:capability}. The capability calculus uses the Euclidean distance $d(i,j)$ between the UAV and the task, the UAV's quality $Q(i,j)$ to perform the task and the weight $\alpha \in [0,1]$ given to the distance and quality factors. 

\begin{equation} \label{eq:tendencia}
	\textrm{T}_{\theta_{ij}}(st_j) = \frac{st_{j}^2}{st_{j}^2 + \theta_{ij}^2}
\end{equation}

\begin{equation} \label{eq:limiar}
	\theta_{ij} = 1 - k_{ij}
\end{equation}

This capability represents the relation among the distance to the task and the sensor's quality to perform it. The sensors quality represents how suitable is the use of a sensor to execute a specific task.

\begin{equation} \label{eq:capability}
\begin{split}
k_{ij} = \frac{\max_{g \in J} \{d(i,g)\} - d(i,j)}{\max_{g \in J} \{d(i,g)\}} \times \alpha + \\
(1 - \frac{\max_{g \in J} \{Q(i,g)\} - Q(i,j)}{\max_{g \in J} \{Q(i,g)\}}) \times (1-\alpha)
\end{split}
\end{equation}

\begin{algorithm}[h!t]
	\caption{Pseudo code - SAL (from Schwarzrock et al.\cite{MAS07})}
	\label{algo:swarm-gap2}
	
	\SetAlgoLined
	\DontPrintSemicolon
	\SetKwBlock{Loop}{loop}{end loop}
	\SetKwFor{ForAll}{for all}{do}{end for}
	
	%\SetAlgoNlRelativeSize{-3}
	\SetNlSty{text}{}{:}
	\SetNlSkip{0.3em}
	
	Receive Token\;
	Compute available resources $r_i $ \; \label{line:compute_rALA}
	
	\ForAll{ available tasks }{ \label{line:forallALA}
		Compute capability $k_{ij}$\; \label{line:compute_kALA}
		Compute tendency $T_{\theta_{ij}}$ \;  \label{line:compute_tALA}
	}
	Sort tasks by descending tendency\; \label{line:sortbyTend}
	
	\ForAll{ available tasks sorted by tendency }{
		\If{ roulette() $< T_{\theta_{ij}(st)}$ and $r_i \geq c_j $}{ \label{line:ini_ifalgo1}
			Allocate task $j$ to agent $i$ \; \label{line:aloca_sgap}
			Decrease resource $r_i $\; \label{line:decrease_r} \label{line:fim_ifalgo1}
		}
	}
	
	The same as lines \ref{line:ALini} to \ref{line:ALfim} of the Algorithm \ref{algo:swarm-gap} \;
	
\end{algorithm}

In the scenario adopted by \textit{Schwarzrock et al.}\cite{MAS07}, each UAV can perform more than one task, but each task can be performed by only one agent. The mission transmission, by a Central Command, is done using a token-based protocol that transmits all information about the tasks and agents association. With this protocol, when a specific UAV chooses a task and allocate it to itself, it sends this information to the next agent of the team. Thus, the next agent will know which tasks are available to be executed. Additionally, \textit{tick} is the unit used to measure the execution time of these algorithms.