\documentclass[review]{elsarticle}

\usepackage[utf8]{inputenc}
\usepackage{lineno,hyperref}

\usepackage{color}
\usepackage{amsmath} % separar equação
%\usepackage[miktex,subfolder,cleanup]{gnuplottex} % Gnuplot
\usepackage{algorithmic}
\usepackage[ruled,lined,noend,linesnumbered]{algorithm2e}
\usepackage{subfigure}
\usepackage{multicol}
\usepackage{color}

\usepackage[inline]{enumitem}

\setlist[enumerate,1]{%
	label=\roman*),ref=\roman*
}

\newlist{inlinelist}{enumerate*}{1}
\setlist*[inlinelist,1]{%
	label=(\alph*),ref=(\alph*)
}

\newcommand{\uav}{UAV}
\newcommand{\uavs}{UAVs}

\def\note#1{\relax}
\definecolor{red}{rgb}{1,0,0}
\definecolor{orange}{rgb}{1,0.5,0}
%\newcommand{\ana}[1]{\textcolor{red}{\textsc{ANA: #1}}}
%\newcommand{\jana}[1]{\textcolor{blue}{\textsc{JANAINA: #1}}}
%\newcommand{\iuli}[1]{\textcolor{green}{\textsc{IULI: #1}}}

\DeclareMathOperator*{\argmax}{arg\,max}

\modulolinenumbers[5]

\journal{Engineering Applications of Artificial Intelligence}

\begin{document}

\begin{frontmatter}
	
\title{Extending a Swarm-GAP based Approach for Dynamic Environments}

%% or include affiliations in footnotes:
\author[unbaddress]{Junier Caminha Amorim}
\ead{junieramorim@aluno.unb.br}

\author[unbaddress]{Vander Alves}
\ead{valves@unb.br}

\author[brazilianarmyaddress]{Ricardo Queiroz de Araujo Fernandes}
\ead{ricardo@cds.eb.mil.br}

\author[ufrgsaddress]{Edison Pignaton de Freitas}
\ead{epfreitas@inf.ufrgs.br}

\address[unbaddress]{Computation Science Department University of Brasilia, Brazil}
\address[ufrgsaddress]{Institute of Informatics Federal University of Rio Grande do Sul, Brazil}
\address[brazilianarmyaddress]{Software Development Center - Brazilian Army, Brazil}
%\linenumbers

\begin{abstract}
Swarm-GAP is an heuristic that combines a swarm intelligence strategy with the generalized assignment problem(GAP) method. This approach is specially appropriate when there are agents in a collaborative job, but heuristics have drawbacks to optimize resources application. A previous work proposed the usage of three variations applied on the swarm-GAP algorithm to solve the problem of tasks allocation among agents representing Unmanned Aerial Vehicles (\uavs) seeking for resources optimization. However it only considered a non-dynamic scenario, where there are no attributes changes during system execution. As the original domain of application is related to military context, where the primary requirement of systems is to support an expected high level of dynamism, it is necessary to consider some kind of attributes changes. Therefore, the contribution of this study is to present an extension of the original work that addresses dynamism to the team's behaviour. In this new scenario, the number of agents (\uavs) changes in runtime and the adaptation occurs to maintain the mission execution in the best possible way. The extension proposed evaluation was done by conducting an independent replication of the original experiments. The resulting evidence shows that some strategies with good quality responses in a static scenario are not capable to maintain a satisfactory quality level in dynamic contexts even under small attribute change. 
\end{abstract}

\begin{keyword}
Unmanned Aerial Vehicles, Task Allocation, Replication
\end{keyword}

\end{frontmatter}

%\linenumbers

\section{Introduction} \label{sec:introduction}
\input{introduction}

\section{Background}\label{sec:background}
\input{background}

\section{Problem formulation}\label{sec:problem}
\input{problem}

\section{Proposed solution}\label{sec:methods}
%\input{methods}

\section{Experimental setup}\label{sec:experimental_setup}
%\input{experimental_setup}

\section{Experimental results and analysis}\label{sec:experimental_result}
%\input{results}

\section{Related work}\label{sec:rw}
%\input{related_work}

\section{Conclusion} \label{sec:conclusions}
%\input{conclusions}

\section*{References}
\bibliographystyle{elsarticle-num}
\bibliography{references}

\end{document}